---
title: "Final Assignment Pitch Slides"
author: ""
date: "2/14/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My app.

This app plots the parabola equation. The parabola usually looks like this:

```{r myplot, fig.align = 'center', fig.cap = 'parabola'}
x = sort(runif(100,-1,1))
y = x^2
plot(x,y, type = "l")
```

## The Equation.

Perhaps the parabola equation makes you think of this: **y = x^2**

But the full equation is actually this: **y = ax^2 + bx + c**

```{r myequation, echo = TRUE}
#So if you create some data as follows:
x = sort(runif(100,-1,1))
y = x^2   

```

This equation will create a parabola with: 

- parameter a = 1 
- parameter b = 0
- parameter c = 0


## What do these parameters do?
Fun things!

- Parameter a will change the direction and width of the parabola
- Patameter b will skew the parabola
- Parameter c will shift the parabola

Sounds fun?

## You try!

https://alenarto.shinyapps.io/assignmentapp/
